% vim:set tw=78 ai:
\documentclass[12pt,a4paper,english,pdftex]{article}
\usepackage[utf8]{inputenc}
\usepackage{babel,fullpage,setspace,calc,tweaklist}
\usepackage[bookmarks=false]{hyperref}
\usepackage{currvita}
\addtolength{\textheight}{0.5cm}

\AtBeginDocument{%
    \settowidth{\cvlabelwidth}{%
        \cvlabelfont 88/8888 -- 88/8888%
    }%
}

\renewcommand{\labelitemi}{--}

\renewcommand{\descripthook}{\setlength{\topsep}{-3pt}%
  \setlength{\itemsep}{-2pt}}
\renewcommand{\itemhook}{\setlength{\topsep}{-3pt}%
  \setlength{\itemsep}{-2pt}}

\begin{document}
\begin{cv}{Curriculum Vitae of Tomáš Janoušek}
    \begin{cvlist}{Personal}
        \item
            Tomáš Janoušek \\
            Kosmákova 35 \\
            615\,00, Brno \\
            Czech Republic
        \item
            Phone: +420\,608\,876\,277 \\
            E-mail: \texttt{tomi@nomi.cz} \\
            Web: \href{http://work.lisk.in/}{\texttt{http://work.lisk.in/}}
        \item
            Place and date of birth: Brno, 8th~April~1987
    \end{cvlist}

    \goodbreak
    \begin{cvlist}{Education}
        \item[09/2006 -- present]
            Masaryk University, Faculty of Informatics \\
            field ``Applied Informatics'' \\
            \href{http://www.fi.muni.cz/}{\texttt{http://www.fi.muni.cz/}}
	    \\[2mm]
	    Member of the Parallel \& Distributed Systems Laboratory since
	    2008
        \item[09/2002 -- 06/2006]
            Grammar school -- Gymnázium Brno, třída Kpt. Jaroše 14 \\
            \href{http://www.jaroska.cz/}{\texttt{http://www.jaroska.cz/}}
    \end{cvlist}

    \goodbreak
    \begin{cvlist}{Work experience (all part-time)}
        \item[09/2007 -- 12/2007]
	    Masaryk University, Faculty of Informatics, Department of Computer
	    Science
            \begin{itemize}
                \item seminar tutor of a course in Functional programming
		\item examiner
            \end{itemize}
        \item[12/2006 -- 04/2008]
            Red Hat Czech s.r.o.
            \begin{itemize}
                \item Software Engineer
                \item RHEL/Fedora package maintainer -- bug fixing,
		implementing new features, integrating software into the
		Fedora distribution, etc.
            \end{itemize}
        \item[11/2002 -- 05/2007]
            Qnet CZ s.r.o.
            \begin{itemize}
                \item Information system development
                \item VoIP deployment
                \item Web development
                \item Network administration (both hardware and software)
            \end{itemize}
    \end{cvlist}

    \goodbreak
    \begin{cvlist}{Language skills}
        \item[Czech] native speaker
        \item[English] advanced written and spoken
        \item[German] basic written
    \end{cvlist}

    \goodbreak
    \begin{cvlist}{Personal skills}
        \item[Driving licence] Group B (Car)
	\item[Social skills] Excellent communication skills both written and
	spoken, experiences giving presentations about IT related topics.

	Great teaching skills, experiences in teaching computer science and
	high school mathematics.

	\item[Organisational skills] Ability to work in a team. Ability to
	catch attention and effectively communicate ideas to a group of
	people.

	\item[Other skills] Excellent ability to learn. Willingness to take
	risks and to explore new possibilities.

	Experiences in proofreading of Czech and English text.
    \end{cvlist}

    \goodbreak
    \begin{cvlist}{Computer skills}
        \item[Programming]
            \begin{description}
                \item[C/C++] advanced knowledge, 10 year exp. (6 year
                work exp.)
		    % since 1998, 2002 resp.
                \item[Haskell] advanced knowledge, 2 year exp.
		    % since 2006
                \item[Perl] advanced knowledge, 5 year exp.
		    % since 2002
                \item[Java] J2SE -- intermediate knowledge, J2ME -- basic
                knowledge, \\ 1 year exp.
		    % accum.
                \item[Bash] intermediate knowledge, 6 year exp.
		    % since 2002
                \item[HTML, CSS, PHP] intermediate knowledge, 6 year exp.
		    % since 2001 ?
                \item[x86 assembler] basic knowledge
                \item[doxygen, javadoc] intermediate knowledge, 2 year exp.
		    % since 2005
            \end{description}

	\goodbreak
        \item[Database]
            \begin{description}
                \item[MySQL] intermediate knowledge, 4 year exp. (4 year work
                exp.)
		    % accum.
                \item[PostgreSQL] basic knowledge
            \end{description}

	\goodbreak
        \item[Version control]
            \begin{description}
		\item[Git] advanced knowledge, 1 year exp.
		    % since 2007
                \item[Subversion] advanced knowledge, 4 year exp.
		    % since 2003
                \item[CVS] intermediate knowledge, 1 year exp.
		    % since 2006
            \end{description}

	\goodbreak
        \item[Networking]
            \begin{description}
                \item[IPv4, IPv6, TCP, UDP] advanced knowledge, 6 year exp.
		    % since 2002
                \item[routing, OSPF, BGP] intermediate knowledge, 3 year exp.
		    % accum
                \item[iptables, tc (Linux QoS)] advanced knowledge, 5 year
                exp.
		    % since 2002
                \item[IP tunneling, OpenVPN] advanced knowledge, 3 year exp.
		    % accum
            \end{description}

	\goodbreak
        \item[Administration]
            \begin{description}
                \item[Linux -- RedHat, Debian] advanced knowledge, 6 year exp.
		    % since 2002
                \item[Linux -- other] advanced knowledge
                \item[FreeBSD] intermediate knowledge %, 1 year exp.
		    % accum
                \item[Windows] intermediate knowledge
            \end{description}

	\goodbreak
        \item[Typesetting]
            \begin{description}
                \item[\LaTeXe] advanced knowledge, 5 year exp.
		    % since 2003
                \item[MS Office, OpenOffice.org] intermediate knowledge
            \end{description}

	%\goodbreak
        \item[Certificates]
            \begin{description}
                \item[Brainbench]
                    \href{http://work.lisk.in/brainbench.cgi}{\texttt{http://work.lisk.in/brainbench.cgi}}
            \end{description}
    \end{cvlist}

    \goodbreak
    \begin{cvlist}{Publications, talks}
        \item[11/2006]
            talk ``MPlayer tips \& tricks'' \\
            LinuxAlt 2006, Brno \\[1mm]
	    A talk about the free MPlayer media player, it's pros and cons,
	    examples of innovative usage and recent features. I gave an
	    English version of this talk later at the Red Hat developer
	    conference, the slides for it are on the link as well. \\[1mm]
            \href{http://tomi.nomi.cz/linuxalt2006/}{\texttt{http://tomi.nomi.cz/linuxalt2006/}}
        \item[01/2006]
            project work ``xchat-bttrw'' \\
            Gymnázium Brno, třída Kpt. Jaroše 14 \\[1mm]
	    A thesis about a webchat client in C++, covering its design, core
	    components, code reference and future work. \\[1mm]
            \href{http://tomi.nomi.cz/xchat-bttrw-doc/}{\texttt{http://tomi.nomi.cz/xchat-bttrw-doc/}}
    \end{cvlist}

    \goodbreak
    \begin{cvlist}{Awards}
        \item[06/2004]
            Winner of the ``Youth championship of the Czech Republic in
            programming'' \\
            \href{http://www.stv.cz/pgm_cr/mcr2004vm.html}{\texttt{http://www.stv.cz/pgm\_cr/mcr2004vm.html}}
    \end{cvlist}

    \goodbreak
    \begin{cvlist}{Hobbies}
        \item swimming, driving, winter sports
    \end{cvlist}

    \enlargethispage{0.3cm}
    \cvplace{Brno}
    \date{\today}
\end{cv}
\end{document}
